Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex

\subsubsection{Depth-Limiting}
To limit the size of trie indexes, an optional maximum depth can be set. If set, words longer than the depth are cut off so that the remainder substrings are stored at the leaves. Figure~\ref{triemax} shows the structure of the same trie as before, but with a maximum depth of 4. Leaf nodes store this substring data as a mapping from substring to document ids containing that substring. During lookups, if the maximum depth of the trie is reached, this map is searched for matches. So while depth-limiting trie indexes can limit the number of trie nodes that need to be traversed upon lookups, they incur the cost of searching these maps at the leaves. If the max depth parameter is too small, these maps can be large and slow down search significantly. If set too large, the max depth parameter has no effect.

@@

\subsection{Depth-Limiting for Tries}
As seen in Figure *****, the maximum depth parameter has an effect on lookup times in trie indexes. The graph shows the results for a trie index prefix search, but the similar results would be expected on suffix searches. A small set of input tweet data was used (367 KB data, about 2100 tweets), and the same three words were looked up in indexes created with differing max depths. The lookup time tends to decrease as the maximum depth increases; this is because depth cutoffs can result in slow searches through word mappings stored on leaf nodes (see section **** for details). The difference in times is more pronounced for the term ``feel'', with a drop from 26.78ms to 18.05ms. For the term ``james'', lookup times are much closer together and not as affected by depth limits. This is due to the fact that ``feel'' yielded many more results (85 results) than ``james'' (4 results), suggesting that more potential matches had to be searched at the leaf nodes for ``feel'' than for ``james''. Results for ``wait'' are between the others, and also show a moderate drop in lookup time as the maximum depth increases. This is most likely because ``wait'' produced a moderate 36 results, and therefore a moderate number of terms were searched at the leaves.

\begin{figure}[h!]
   \includegraphics[scale=.43]{trie_maxdepth_graph}
  \caption{Maxiumum depth vs lookup times for a prefix trie index. A depth of ``None'' indicates that there is no limit. The results for three different search terms are shown. The dataset size was roughly 2100 tweets.}
\end{figure}

>>>>

\subsubsection{Depth-Limiting}
\label{depthlimit}
To limit the size of trie indexes, an optional maximum depth can be set. If set, words longer than the depth are cut off so that the remainder substrings are stored at the leaves. Figure~\ref{triemax} shows the structure of the same trie as before, but with a maximum depth of 4. Leaf nodes store this substring data as a mapping from substring to document ids containing that substring. During lookups, if the maximum depth of the trie is reached, this map is searched for matches. So while depth-limiting trie indexes can limit the number of trie nodes that need to be traversed upon lookups, they incur the cost of searching these maps at the leaves. If the max depth parameter is too small, these maps can be large and slow down search significantly. If set too large, the max depth parameter has no effect.

@@

\subsection{Depth-Limiting for Tries}
As seen in Figure~\ref{comptrie}, the maximum depth parameter has an effect on lookup times in trie indexes. The graph shows the results for a trie index prefix search, but the similar results would be expected on suffix searches. A small set of input tweet data was used (367 KB data, about 2100 tweets), and the same three words were looked up in indexes created with differing maximum depths. The lookup time tends to decrease as the maximum depth increases; this is because depth cutoffs can result in slow searches through word mappings stored on leaf nodes (see Section~\ref{depthlimit} for details). The difference in times is more pronounced for the term ``feel'', with a drop from 26.78ms to 18.05ms. For the term ``james'', lookup times are much closer together and not as affected by depth limits. This is due to the fact that ``feel'' yielded many more results (85 results) than ``james'' (4 results), suggesting that more potential matches had to be searched at the leaf nodes for ``feel'' than for ``james''. Results for ``wait'' are between the others, and also show a moderate drop in lookup time as the maximum depth increases. This is most likely because ``wait'' produced a moderate 36 results, and therefore a moderate number of terms were searched at the leaves.

\begin{figure}[h!]
   \includegraphics[scale=.43]{trie_maxdepth_graph}
  \caption{Maximum depth vs lookup times for a prefix trie index. A depth of ``None'' indicates that there is no limit. The results for three different search terms are shown. The dataset size was roughly 2100 tweets.}
\label{comptrie}
\end{figure}
